Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-21 snapshot_system/intro.tex

\section{Introduction}
In a cluster-based cloud environment,
% such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
%Backup  of virtual disks is relatively straightforward since
%these image files are stored as regular files from the external point of view,
%backing up VM's data is mainly done by taking snapshots of virtual disk images.
%A snapshot preserves the data of a VM's file system at a specific point in time. 
%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.
The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand. 
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
(see Figure~\ref{fig:traditional-arch})
can effectively identify and remove content duplicates among snapshots, 
but the solution can be expensive. There is also a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/traditional-arch.pdf}
    \label{fig:traditional-arch}
    \caption{Traditional VM Backup System}
\end{figure}

This paper seeks for a low-cost architecture option and takes advantage of the
fact that the
backup service collocates on the cloud cluster with a minimum resource usage (see Figure~\ref{fig:colocated-arch})
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
%On the other hand, comparing fingerprints  adds significant  memory cost. 
%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
Cloud providers often wish that the backup service only consumes  small or modest resources
with a minimal impact to the existing cloud services.  
We study and evaluate the integration of several deduplication strategies to meet
the low-cost collocation requirement. In parallel, we identify deduplication options that yield
better fault isolation.
%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
We achieve improved fault isolation by accounting for the fact that after
deduplication most data blocks are shared by several to many virtual machines.
Failure of such popluar blocks would have a catastrophic effect and many
snapshots of virtual machines would be affected.
The previous work in deduplication focuses mainly on the efficiency and approximation of
finger print comparison, and has not addressed fault tolerance along with a low-cost solution.
Another issue considered is that
%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots compete for computing resources as well so deletion needs
to be considered in system design. The additional complexity for deletions
come from the dependencies created by multiple links to the same problem, so
some solution is needed to determine blocks with no dependent snapshots after deletion.
% especially when  VMs can migrate around in the cloud.

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/colocated-arch.pdf}
    \label{fig:colocated-arch}
    \caption{Colocated VM Backup System}
\end{figure}

>>>>

\section{Introduction}
In a cluster-based cloud environment,
% such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
%Backup  of virtual disks is relatively straightforward since
%these image files are stored as regular files from the external point of view,
%backing up VM's data is mainly done by taking snapshots of virtual disk images.
%A snapshot preserves the data of a VM's file system at a specific point in time. 
%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.
The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand. 
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
(Figure~\ref{fig-traditional-arch})
can effectively identify and remove content duplicates among snapshots, 
but the solution can be expensive. There is also a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/traditional-arch.pdf}
    \label{fig-traditional-arch}
    \caption{Traditional VM Backup System}
\end{figure}

This paper seeks for a low-cost architecture option and takes advantage of the
fact that the
backup service collocates on the cloud cluster with a minimum resource usage
(Figure~\ref{fig-colocated-arch})
%Since most of backup data is not used in practice, system resource in such a service is not fully utilized.
%The dirty bit approach~\cite{??}  which checks the version difference can effectively remove
%duplicates while using content fingerprints can significantly compress more~\cite{Bottlneck08}.
%On the other hand, comparing fingerprints  adds significant  memory cost. 
%Since each physical machine in a cluster  hosts many VMs, memory contention happens frequently.
Cloud providers often wish that the backup service only consumes  small or modest resources
with a minimal impact to the existing cloud services.  
We study and evaluate the integration of several deduplication strategies to meet
the low-cost collocation requirement. In parallel, we identify deduplication options that yield
better fault isolation.
%A recent study using subsampling~\cite{Guo2011}  can significantly reduce the memory requirement.
We achieve improved fault isolation by accounting for the fact that after
deduplication most data blocks are shared by several to many virtual machines.
Failure of such popluar blocks would have a catastrophic effect and many
snapshots of virtual machines would be affected.
The previous work in deduplication focuses mainly on the efficiency and approximation of
finger print comparison, and has not addressed fault tolerance along with a low-cost solution.
Another issue considered is that
%that deletion of old snapshots compete for computing resource as well. That is because data dependence created
deletion of old snapshots compete for computing resources as well so deletion needs
to be considered in system design. The additional complexity for deletions
come from the dependencies created by multiple links to the same problem, so
some solution is needed to determine blocks with no dependent snapshots after deletion.
% especially when  VMs can migrate around in the cloud.

\begin{figure}[htb]
    \centering
    \includegraphics[width=3in]{images/colocated-arch.pdf}
    \label{fig-colocated-arch}
    \caption{Colocated VM Backup System}
\end{figure}
